Deriving Multi-Headed Projective Dependency Parses \\ from Link Grammar Parses

### 2014-07-08 doc/LinksToDAG.tex
reenabled the TODO comments in the paper. Commented one out (making the longtable at the end in the appendix).
added reviews-initial.txt
updated the paper such that the russian numbers are automatically generated.

\section{Data Sets}
We used the English sentences from the CoNLL 2007 Shared Task \cite{CONLL-SHARED-2007}---a subset of the Penn Treebank for which {\em single}-headed reference parses are available.  We also used a prefix of the Russian National Corpus,\footnote{That is, a prefix when considering the files in Unix sort order by filename.  We dropped sentences with $\leq 2$ words, as well as file 22592319, which appeared to contain charts.} which is unparsed.

We generated link parses using the AbiWord/CMU link grammar parser version 5.0.8 \cite{LINKPARSER-2014}.  The parser's coverage is not perfect: we obtained connected parses for only \input{figure/conll_analysis_sentences_total.tex}(of \input{figure/conll_analysis_sentences_original.tex}$\!\!$) English sentences and only 8,018 (of 10,000) Russian sentences, discarding the other sentences.\footnote{For Russian only, we permitted the parser to drop words if necessary.  Otherwise only 208 sentences were parseable.}
These two languages have the most mature lexicons at present, although lexicons for 7 other languages are available.

@@

We solved our ILP problem using the SCIP Optimization Suite \cite{achterberg2009scip}, encoding it using the ZIMPL language \cite{Koch2004}.  Our largest run took 1.5 hours. \noteJH{A run of 10,000 sentences takes 3142 seconds (update in final version!)}  Detailed results from this run are included as Appendix~\ref{app:linktypes}.  On English, only \input{figure/allowed_labels_both.tex}of \input{figure/allowed_labels_total.tex}link {\em types} allowed both directions, and only $\sum_{ij} s_{ij} = \input{figure/label_token_disallowed}$ of \input{figure/label_token_total}link {\em tokens} required a disallowed direction via slack.
\input{figure/conll_analysis_sentences_multiheaded}of the English sentences but only 0.15\% of the Russian ones had at least one multiheaded word.
\noteJE{2 significant digits is enough}
\noteJE{update these numbers}

@@

\newpage
\bibliographystyle{acl2014}
\bibliography{LinksToDAG}

@@

Recall that \url{http://www.abisource.com/projects/link-grammar/dict/summarize-links.html} documents the 122 link types in the English link grammar lexicon.  Below is the result of our largest English run, whose corpus uses 107 of these types. \noteJH{automatically generate this number}

@@

\NoteJE{improve table formatting.  Numeric justification; en dashes; longtable; remove most hlines.}

>>>>

\section{Data Sets}
We used the English sentences from the CoNLL 2007 Shared Task \cite{CONLL-SHARED-2007}---a subset of the Penn Treebank for which {\em single}-headed reference parses are available. 
%We also used a prefix of the Russian National Corpus,\footnote{That is, a prefix when considering the files in Unix sort order by filename.  We dropped sentences with $\leq 2$ words, as well as file 22592319, which appeared to contain charts.} which is unparsed.
We also used a prefix of the Russian News Commentary data from the ACL 2013 Shared Task of Machine Translation,\footnote{\url{http://www.statmt.org/wmt13/training-monolingual-nc-v8.tgz}} which is unparsed.

We generated link parses using the AbiWord/CMU link grammar parser version 5.0.8 \cite{LINKPARSER-2014}.  The parser's coverage is not perfect: we obtained connected parses for only \input{figure/conll_analysis_sentences_total.tex}(of \input{figure/conll_analysis_sentences_original.tex}$\!\!$) English sentences and only \input{figure/russian_sentence_count.tex}(of \input{figure/russian_original_sentence_count.tex}$\!\!$) Russian sentences, discarding the other sentences.
These two languages have the most mature lexicons at present, although lexicons for 7 other languages are available.

@@

We solved our ILP problem using the SCIP Optimization Suite \cite{achterberg2009scip}, encoding it using the ZIMPL language \cite{Koch2004}.  Our largest run took 1.5 hours. \noteJH{A run of 10,000 sentences takes 3142 seconds (update in final version!)}  Detailed results from this run are included as Appendix~\ref{app:linktypes}.  On English, only \input{figure/allowed_labels_both.tex}of \input{figure/allowed_labels_total.tex}link {\em types} allowed both directions, and only $\sum_{ij} s_{ij} = \input{figure/label_token_disallowed}$ of \input{figure/label_token_total.tex}link {\em tokens} required a disallowed direction via slack.
\input{figure/conll_analysis_sentences_multiheaded.tex}of the English sentences but only \input{figure/russian_multiheaded.tex}of the Russian ones had at least one multiheaded word.
%\noteJE{2 significant digits is enough}
%\noteJE{update these numbers}

@@

% \newpage
\bibliographystyle{acl2014}
\bibliography{LinksToDAG}

@@

Recall that \url{http://www.abisource.com/projects/link-grammar/dict/summarize-links.html} documents the 122 link types in the English link grammar lexicon.  Below is the result of our largest English run, whose corpus uses \input{figure/allowed_labels_total.tex}of these types. \noteJH{automatically generate this number correctly: 107}

@@

%\NoteJE{improve table formatting.  Numeric justification; en dashes; longtable; remove most hlines.}
